---
title: "DEA_ssudalag"
output: html_document
---
#Hope Valley Health Care Association Data Envelopment Analysis(DEA)
### Inputs = Staff Hours per day, Supplies per day
### Outputs = Reimbursed Patient-Days, Privately paid patient days

```{r}
library("Benchmarking")
```

```{r}
x <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2.0,1.2,0.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
x
y
colnames(x) <- c("Staff hours per day","Supplies per day")
colnames(y) <- c("Reimbursed patient-days","Privately paid patient days")
x
y
```

## DEA with RTS = FDH
```{r}
d <- dea(x,y,RTS = "FDH")
d

```
### peers
```{r}
peers(d)
```
### lambdas
```{r}
lambda(d)
```

### plot
```{r}

dea.plot.frontier(x,y,RTS = "FDH")
```

### The results for the Data envelopment analysis using the FDH shows that there are no ineffecient facilities


## DEA with RTS = CRS

```{r}
d <- dea(x,y,RTS = "CRS")
d
```

### peers
```{r}
peers(d)
```
### lambdas

```{r}
lambda(d)
```

### plot

```{r}
dea.plot.frontier(x,y,RTS = "CRS")
```

### The results for the Data envelopment analysis using the CRS shows that facility 5 and facility 6 are ineffecient facilities and their peers are facility 1,2,4 and lambda shows the weightage on each of the facilities


## DEA with RTS = VRS

```{r}
d <- dea(x,y,RTS = "VRS")
d
```

### peers
```{r}
peers(d)
```

### lambdas
```{r}
lambda(d)
```

### plot
```{r}
dea.plot.frontier(x,y,RTS = "VRS")
```

### The results for the Data envelopment analysis using the VRS shows that facility 6 is ineffecient facility and the peers are facility 1,2,5 and lambda shows the weightage on each of the facilities


## DEA with RTS = IRS
```{r}
d <- dea(x,y,RTS = "IRS")
d
```

### peers
```{r}
peers(d)
```

### lambdas
```{r}
lambda(d)
```

### plot

```{r}
dea.plot.frontier(x,y,RTS="IRS")
```

### The results for the Data envelopment analysis using the IRS shows that facility 6 is ineffecient facility and the peers are facility 1,2,5 and lambda shows the weightage on each of the facilities


## DEA with RTS = DRS

```{r}
d <- dea(x,y,RTS = "DRS")
d
```

### peers
```{r}
peers(d)
```

### lambdas
```{r}
lambda(d)
```

### plot
```{r}
dea.plot.frontier(x,y,RTS = "DRS")
```

### The results for the Data envelopment analysis using the DRS shows that facility 5 and facility 6 are ineffecient facilities and their peers are facility 1,2,4 and lambda shows the weightage on each of the facilities


## DEA with RTS = FRH
```{r}
d <- dea(x,y,RTS = "fdh+")
d

```
### peers
```{r}
peers(d)
```

### lambdas
```{r}
lambda(d)
```

### plot
```{r}
dea.plot.frontier(x,y,RTS = "fdh+")
```

### The results for the Data envelopment analysis using the FRH shows that there are no ineffecient facilities


## Sumarising the results in tabular format. Inefficient = inefficient facilities
## P1,P2,P3  = Peers
## L1,L2,L3,L4,L5,L6 = Lambda


```{r}
i <- matrix(c(0,5,6,6,6,5,6,0,NA,1,1,1,1,1,1,NA,NA,2,2,2,2,2,2,NA,NA,4,4,5,5,4,4,NA,0,0.20,0.34,0.40,0.40,0.20,0.34,0,0,0.08,0.39,0.34,0.34,0.08,0.39,0,0,0,0,0,0,0,0,0,0,0.53,0.13,0,0,0.53,0.13,0,0,0,0,0.25,0.25,0,0,0,0,0,0,0,0,0,0,0),ncol = 10)
rownames(i) <- (c("FDH","CRS","CRS","VRS","IRS","DRS","DRS","FRH"))
colnames(i) <- c("Inefficient","P1","P2","P3","L1","L2","L3","L4","L5","L6")
result <- as.table(i)
library(knitr)
kable(result,caption = "DEA")
```
































